 

### 2021-05-03 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below (easiest in alphabetical order)
```
---
nocite: | 
  @mau_temperate_2018; @hernandezSimilarTemperatureDependence2020; @cobleHowVerticalPatterns2016a; @slotPhotosyntheticHeatTolerance2019; @valladaresShadeToleranceKey2008b; @beaumontVerticalGradientsLeaf2009; @sackHowStrongIntracanopy2006,@cobleLightDrivesVertical2014; @scartazzaInvestigatingEuropeanBeech2016; @martinCovarianceSunShade2020; @bolstad_foliar_1999; @harleyEffectsLightTemperature1996; @kullDistributionLeafPhotosynthetic1998; @kafutiFoliarWoodTraits2020; @duursmaVerticalCanopyGradients2006; @cobleLightDrivesVertical2014a; @vanwittenbergheVariabilityStomatalConductance2012; @poorterLeafOpticalProperties1995; @poorterMetaanalysisPlantResponses2019b; @cavaleri_foliar_2008; @niinemetsAcclimationHighIrradiance1998; @panditharathnaChangeLeafStructure2008; @baltzerLeafOpticalResponses2005; @kusiPlasticLeafMorphology2020
---

>>>>

```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below (easiest in alphabetical order)
```
---
nocite: |
@mau_temperate_2018; @cobleLightDrivesVertical2014; @sackHowStrongIntracanopy2006; @chinLeafAcclimationLight2017; @wykaResponsesLeafStructure2012; @athertonSpatialVariationLeaf2017; @kenzoHeightrelatedChangesLeaf2015; @kusiPlasticLeafMorphology2020; @dangProfilesPhotosyntheticallyActive1997;@gebauerEffectsProlongedDrought2015; @marencoLeafTraitPlasticity2017; @kafutiFoliarWoodTraits2020; @vanwittenbergheVariabilityStomatalConductance2012; @zhang_photosynthetic_2012; @weerasingheCanopyPositionAffects2014; @oldhamHydrostaticGradientNot2010; @ichieEcologicalDistributionLeaf2016; @gregoriouEffectsReducedIrradiance2007; @levizouNondestructiveAssessmentLeaf2005; @liakouraTrichomeDensityIts1997; @fauset_differences_2018; @niinemetsAcclimationHighIrradiance1998; Ishida et al. 1999; @millenLeafAngleAdaptive1979; @smithShootStructuralEffects1988; @hadleyInfluenceKrummholzMat1987; @panditharathnaChangeLeafStructure2008; @baltzerLeafOpticalResponses2005; @dietzVerticalPatternsDuration2007; @cobleHowVerticalPatterns2016a; @scartazzaInvestigatingEuropeanBeech2016; @duursmaVerticalCanopyGradients2006; @harleyEffectsLightTemperature1996; @hernandezSimilarTemperatureDependence2020; @turnbullScalingFoliarRespiration2003; @chenLeafEconomicsSpectrum2020; @vandewegPhotosyntheticParametersDark2012; @cavaleri_foliar_2008; @konigerXanthophyllCyclePigmentsPhotosynthetic1995;@matsubaraSunshadePatternsLeaf2009; Harris and Medina 2013; @hansenVariationPigmentComposition2002a; @poorterLeafOpticalProperties1995; @cobleHowVerticalPatterns2016; @niinemetsCanopyGradientsLeaf2004; @poorterLeafOpticalProperties2000
---
